Report

### 2021-01-27 report.Rmd
New model prediction plot + outline introduction

#theme_set(theme_cowplot())
```

@@

## Links betwenn temporal dynamics

@@

## The three model

1. $dN = dB + dB \times B + dB^2 + dB^2 \times B$

3. $dN = dB + B + dB \times B + Inc + Inc \times dB + dB \times B \times Inc$

@@

### Results

- Species richness:
  - decreases a lot in time when biomass decreases
  - increases slightly in time when biomass increases (immigration debt)
  - No effect of community size! (same for the number of nodes)

- Avg trophic level:
  - decreases simultaneously with biomass decreases 
  - increase simultaneously with biomass increases but increases less for bigger
    communities
  - meaning that biomass loss and gain are located in the highest trophic level
    (except gain of biomass in biggest communities)

- Connectance:
  - do not decrease when biomass decreases in little communities
  - decreases when biomass decreases in big communities
  - do not vary when biomass increases

- Weighted connectance:
  - increases (more even flux distribution) when biomass decreases in little communities
  - decreases (more skewed flux distribution) when biomass decreases in big communities
  - decreases when biomass increases

### Summary of result

- There are a significant link between the dynamics of community biomass and the
  dynamics of community structure for all the variables: species richness,
  average trophic level, connectance and weighted connectance.

- We found that the link between network temporal dynamics and biomass temporal
  dynamics change according if the community loses or gain biomass, for all
  variables.

- We found that the biomass of the community at the beginning of the temporal
  series, i.e. community size, had an effect on the link between network
  dynamics and biomass expect for species richness. We also found that the
  effect of biomass was stronger in communities losing biomass for connectance and
  weighted connectance but stronger in communities gaining biomass for average
  trophic level

### Answer to research questions

- Lost and gain of biomass result in different network structure dynamics,
  suggesting that the two processes are not symmetric.
- The effect of community size suggests that the architecture of the community
  in terms of species richness, number of piscivorous species, plays a role in
  its dynamics

### Interpretation

- Richness:
  - When biomass increases, one can that species richness increases as well
    as when biomass decreases conjointly to species richness.
  - Increase in species richness necessitates colonization events, i.e.
    stochastic events while decreases in species richness necessitates
    disparition of species already in the community. Thus, the colonization
    process needs element exterior to the community.
    - Immigration debt: (might be relevant if low availability of new species)
  - second explanation: when biomass increases, competitive interactions may prevent the increase in
    species richness. We expect that processes based on competition would raise
    the role of community size.

- Avg trophic level: 
  - Higest trophic level concentrates most of the biomass, so gain and loss are
    statistically more linked to them
  - In biggest communities, there was no link between biomass and avg trophic
    level dyn because those communities already contain high trophic
    levels (There is a positive correlation between the number of pisc node and
    biomass of the community). So, there is a saturation at the top of the
    chain.
    - The observation that the number of link and link density follow the same
      pattern confirm this interpretation.

@@

```{r}
loadd(predict_plot2)
pred_plot_signif_com <- predict_plot2 %>%
  filter(
    y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
    x == "log_bm_std"
  )
legend_signif <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_signif_com$pred_plot,
  labels = pred_plot_signif_com$y, nrow = 2
)
pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_rich <- predict_plot2 %>%
  filter( y %in% c(get_com_str_var(), "bm_std", "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
  filter(!y %in% "rich_std")
legend_signif <- get_legend(
  pred_plot_rich$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_rich$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_rich$pred_plot,
  labels = pred_plot_rich$y
)
pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_other <- predict_plot2 %>%
  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x %in% c("ct_ff", "w_trph_lvl_avg"))
legend_signif <- get_legend(
  pred_plot_other$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_other$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_other$pred_plot,
  labels = pred_plot_other$y, nrow = 2
)
pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r, fig.dim = c(12, 12)}
plot_grid(
  pred_plot1, plot_grid(pred_plot2, pred_plot3, ncol = 2, rel_widths = c(.75, 1)),
  nrow = 2
)
```

```{r, fig.dim = c(10, 5)}
loadd(betapart_bin, rigal_classification, st_mono_trends_combined_list)

@@

```{r}
# Rich and rich slope
loadd(summary_var_f3y)

@@

```{r}
loadd(model_log_bm_f3y_table_medium)
model_log_bm_f3y_table_medium[["anova_table"]] %>%
  filter( y %in% c(get_com_str_var(), "ct_ff", "log_rich_std")) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

>>>>

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
theme_get()
```

@@

# Introduction

1. Option1 Global change -> change of biomass 
   Option2 Ecological communities are dynamics + example

2. Ecological communities often describe by their richness, biomass

3. BEF

@@

@@

- Species richness, Avg trophic level, connectance:
  - increases when biomass increases while decreases when biomass decreases
  - Avg trophic level: same for species richness  
  - connectance:  decreases when richness increases while increases when
    richness decreases (reverse sign compared to biomass)

- Pielou (eveness) :
  - Indiv: 
    - do not varies with biomass temporal trends
    - increases with increasing temporal trends of species richness
  - Biomass: 
    - increase when biomass decreases and decreases when biomass increases
    - decreases when species richness decreases and increase when species
      richness increases

- Connectance: positive relationship with avg trophic level temporal trends

# Discussion

## Summary of result

- There was a significant positive link between the dynamics of community biomass and the
  dynamics of community structure for the variables: species richness, average trophic level, connectance except for pielou of
  individuals and pielou of biomass which had respectively a no and a negative
  relationship.

- There was a significant positive link between the dynamics of species richness and the
  dynamics of community structure for the variables: average trophic level, connectance, pielou of
  individuals and pielou of biomass; except for connectance which had a negative
  relationship.

- There are a significant link between the dynamics of community biomass and the
  dynamics of community structure for all the variables expect pielou of
  biomass: species richness, average trophic level, connectance and pielou of
  individuals

- We found that the link between network temporal dynamics and biomass temporal
  dynamics **does not change** according if the community loses or gain biomass, for all
  variables.

## Answer to research questions

- Lost and gain of biomass or species richness resulted in same network structure dynamics,
  suggesting that the two processes are symmetric.
- The low effect of community size suggests that the architecture of the
  community in terms of species richness, number of piscivorous species, plays a
  role in its dynamics

## Interpretation

- Richness:
  - When biomass increases, species richness increases as well
    as when biomass decreases conjointly to species richness.

- Avg trophic level: 
  - Higest trophic level concentrates most of the biomass, so gain and loss are
    statistically more linked to them
  - Low and gain of biomass are linked to big individuals

    - The observation that the number of link and link density follow the same
      pattern confirm this interpretation.

@@

```{r}
loadd(predict_plot2)
pred_plot_signif_com <- predict_plot2 %>%
  filter(
    y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
    !y %in% c("bm_std", "rich_std"),
    x == "log_bm_std"
  )
legend_signif <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com %<>% 
  mutate(
  pred_plot = pmap(list(pred_plot, y, x),
    function(p, y, x) {
      # Replace label
      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
      p +
	labs(x = label[1], y = label[2]) +
	theme(legend.position = "none")
    } )
  )

list_p <- pred_plot_signif_com$pred_plot
list_p[[length(list_p) + 1]] <- legend_signif

pred_plot1 <- plot_grid(
  plotlist = list_p,
  labels = "AUTO",
  nrow = 2
)
#pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_rich <- predict_plot2 %>%
  filter( y %in% c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
  filter(!y %in% c("rich_std"))
legend_signif <- get_legend(
  pred_plot_rich$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_rich %<>% 
  mutate(
  pred_plot = pmap(list(pred_plot, y, x),
    function(p, y, x) {
      # Replace label
      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
      p +
	labs(x = label[1], y = label[2]) +
	theme(legend.position = "none")
    } )
  )

list_p <- pred_plot_rich$pred_plot
list_p[[length(list_p) + 1]] <- legend_signif

pred_plot2 <- plot_grid(
  plotlist = list_p,
  nrow = 2,
  labels = "AUTO" 
)
#pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}

pred_plot_other <- predict_plot2 %>%
  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x %in% c("ct_ff", "w_trph_lvl_avg"))
legend_signif <- get_legend(
  pred_plot_other$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_other %<>% 
  mutate(
  pred_plot = pmap(list(pred_plot, y, x),
    function(p, y, x) {
      # Replace label
      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
      p +
	labs(x = label[1], y = label[2]) +
	theme(legend.position = "none")
    } )
  )

list_p <- pred_plot_other$pred_plot
list_p[[length(list_p) + 1]] <- legend_signif

pred_plot3 <- plot_grid(
  plotlist = list_p,
  labels = "AUTO", nrow = 2
)
#pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r, fig.dim = c(10, 7)}
pred_plot1
pred_plot2
pred_plot3
```

```{r, eval = FALSE, fig.dim = c(12, 12)}
plot_grid(
  , plot_grid(, , ncol = 2, rel_widths = c(.75, 1)),
  nrow = 2
)
```

```{r, eval = FALSE, fig.dim = c(10, 5)}
loadd(betapart_bin, rigal_classification, st_mono_trends_combined_list)

@@

@@

```{r}
loadd(model_log_bm_f3y_table_medium)
model_log_bm_f3y_table_medium[["anova_table"]] %>%
  filter(
    y %in% c(get_com_str_var(), "ct_ff", "log_rich_std"),
    !y %in% "rich_std") %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B. The community structure versus the
      biomass"
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
loadd(model_log_rich_f3y_table_medium)
model_log_rich_f3y_table_medium[["anova_table"]] %>%
  filter(
    y %in% c(get_com_str_var(), "log_bm_std"),
    !y %in% "rich_std") %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B. The community structure versus the
      species richness"
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
# Rich and rich slope
loadd(summary_var_f3y, st_mono_trends_combined_list, rigal_classification)
